\documentclass[10pt]{article}
%\usepackage{showframe}	% for deebug purposes
\usepackage{extsizes} % so 9pt can be used for general font size
\pagestyle{empty}    % remove page counter

\usepackage{geometry}    % page geometry
\geometry{a4paper, left=20mm, right=30mm, top=15mm, bottom=15mm}

\usepackage{hyperref} % colored hyperlinks
\hypersetup{colorlinks=true,urlcolor=cyan} % color clickable stuff cyan

\usepackage{enumitem}    % for pretty lists
\setlist{noitemsep, align=right, leftmargin=1em, topsep=0pt}

\renewcommand{\familydefault}{\sfdefault}
% set global font to sans serif family
\setlength\parindent{0pt}    % remove paragraph indent

\usepackage{titlesec}    % for correct header sizes
\titleformat
{\section}    % command
{\fontsize{14pt}{14pt}\bfseries} % format
{\thesection} % label
{1em}    % separation
{}
\titleformat
{\subsection} % command
{\fontsize{11pt}{6pt}\bfseries} % format
{\thesubsection} % label
{1em}    % separation
{}

\titlespacing\section{0pt}{0pt}{10pt}
\titlespacing\subsection{0pt}{10pt}{0pt}

\usepackage{xcolor}    % to use gray color
\usepackage{fontawesome}

\def\changemargin#1#2{\list{}{\rightmargin#2\leftmargin#1}\item[]}
\let\endchangemargin=\endlist
\newcommand{\lmvalue}{5mm}
\newcommand{\rmvalue}{0mm}

\begin{document}

\begin{minipage}[b]{0.78\linewidth}
	{\fontsize{28pt}{28pt}\selectfont Viktor Vorobev}
	\\[1em]
	{\color{gray}\fontsize{16pt}{16pt}\selectfont System Software Tech Lead}
\end{minipage}
\hfill%
\begin{minipage}[b]{0.24\linewidth}
	\begin{flushleft}
		\begin{itemize}
			\item[\color{cyan}\faPaperPlane] \href{https://t.me/vikeyer}{@vikeyer}
			\item[\color{cyan}\faEnvelope] \href{mailto:vikeyer@gmail.com}{vikeyer@gmail.com}
			\item[\color{cyan}\faGithub] \href{https://github.com/viktorvorobev}{viktorvorobev}
			\item[\color{cyan}\faLinkedin] \href{https://www.linkedin.com/in/mr-viktor-vorobev/}{mr-viktor-vorobev}
			\item[\faBuildingO] Budapest, Hungary
		\end{itemize}
	\end{flushleft}
\end{minipage}
\vspace{3mm}
\section*{Cover letter}
\begin{changemargin}{\lmvalue}{\rmvalue}
	9+ years in the field of commercial products. \\
	Expertise in Python backend (Flask, Django, FastAPI), and Frontend (TypeScript, VUE).
	I've developed plenty of different scripts and applications that greatly work in production.
	I also know CI/CD stuff: successfully set up several pipelines.
	Experience using Docker containers, GitHub actions, GitLab actions, Travis CI. \\
	Happy to make customers happy and solve their problems.
	Will always do my best to help my team and make sure that the quality of our product is as good as possible.
	You give me a task, I get it done.
\end{changemargin}
\end{document}
