\documentclass[10pt]{article}
%\usepackage{showframe}	% for deebug purposes
\usepackage{extsizes} % so 9pt can be used for general font size
\pagestyle{empty}    % remove page counter

\usepackage{geometry}    % page geometry
\geometry{a4paper, left=20mm, right=30mm, top=15mm}

\usepackage{hyperref} % colored hyperlinks
\hypersetup{colorlinks=true,urlcolor=cyan} % color clickable stuff cyan

\usepackage{enumitem}    % for pretty lists
\setlist{noitemsep, align=right, leftmargin=1em, topsep=0pt}

\renewcommand{\familydefault}{\sfdefault}
% set global font to sans serif family
\setlength\parindent{0pt}    % remove paragraph indent

\usepackage{titlesec}    % for correct header sizes
\titleformat
{\section}    % command
{\fontsize{14pt}{14pt}\bfseries} % format
{\thesection} % label
{1em}    % separation
{}
\titleformat
{\subsection} % command
{\fontsize{11pt}{6pt}\bfseries} % format
{\thesubsection} % label
{1em}    % separation
{}

\titlespacing\section{0pt}{0pt}{10pt}
\titlespacing\subsection{0pt}{10pt}{0pt}

\usepackage{xcolor}    % to use gray color
\usepackage{fontawesome}

\def\changemargin#1#2{\list{}{\rightmargin#2\leftmargin#1}\item[]}
\let\endchangemargin=\endlist
\newcommand{\lmvalue}{5mm}
\newcommand{\rmvalue}{0mm}

\begin{document}

    \begin{minipage}[t]{0.78\linewidth}
    {\fontsize{28pt}{28pt}\selectfont Viktor Vorobev}
        \\[1em]
        {\color{gray}\fontsize{16pt}{16pt}\selectfont Senior Software Developer}
    \end{minipage}
    \hfill%
    \begin{minipage}[t]{0.24\linewidth}
        \begin{flushleft}
            \begin{itemize}
                \item[\color{cyan}\faEnvelope] \href{mailto:vikeyer@gmail.com}{vikeyer@gmail.com}
                \item[\color{cyan}\faGithub] \href{https://github.com/viktorvorobev}{viktorvorobev}
                \item[\color{cyan}\faLinkedin] \href{https://www.linkedin.com/in/mr-viktor-vorobev/}{mr-viktor-vorobev}
                \item[\faBuildingO] Belgrade, Serbia
            \end{itemize}
        \end{flushleft}
    \end{minipage}

    \vspace{3mm}
    \section*{Summary}
    \begin{changemargin}{\lmvalue}{\rmvalue}
        5 years in the field of commercial products.
        Happy to make customers happy and solve their problems.
        Keen on learning new technologies and take the best of their approaches.
        Will always do my best to help my team and make sure that the quality of our product is as good as possible!
    \end{changemargin}
	\section*{Technologies}
	\begin{changemargin}{\lmvalue}{\rmvalue}
	    Technologies I'm familiar with:\\
        Python, Flask, Django, asyncio, pytest, Socket.IO, REST, Redis, Bash, GIT, Linux,
        Docker, Yocto, \\
        TypeScript, VUE, C++.
    \end{changemargin}
    \section*{Work experience}
    \begin{changemargin}{\lmvalue}{\rmvalue}
        \subsection*{Senior System Software Developer \hfill {\color{gray}Dec 2018 –
        Present}}
        \href{https://emlid.com}{Emlid}

        Backend development for embedded devices.
        Mostly Python (Flask), bash scripts, Redis.
        Creating Systemd services.
        Setup simple CI pipelines using Travis and GitHub actions.
        Design and implementation of REST and SocketIO APIs.
        \begin{itemize}
            \item Hunted down and fixed several memory leaks and CPU hungry
            processes
            \item Significantly improved stability of the newly produced
            code by covering existing systems with tests
            \item Started process of writing documentation for API of the
            codebase
            \item Implemented and reworked configuration applying
            mechanisms which allowed piece-by-piece changes, instead of applying the whole
            configuration at once.
            This opened a way for complete rework of the user applications
            \item Implemented tests for internal migrations' system, and
            then managed to reduce amount of required tests from more than 100 to just 8
            \item Learned different languages (JavaScript, TypeScript) when
            it was necessary for the team.
            Successfully implemented new features using them
        \end{itemize}

        \subsection*{Developer \hfill {\color{gray}Jun 2015 – Dec 2018}}
        \href{https://er.rtc.ru/en/}{Russian State Scientific Center for
        Robotics and Technical Cybernetics}
        \begin{itemize}
            \item Developed
            \href{https://github.com/RTC-SCTB/cuptimer}{Timer} - Python 3 application for
            Linux (Raspbian, Ubuntu), which was used later in the contest "RTC~Cup"
            \item Developed Python 3 module using C++, which allows getting
            data from flight controller Naza M v2 through CAN~interface (It's
            \href{https://github.com/viktorvorobev/NazaCanDecoder}{open source} now)
            \item Developed and programmed several robotic platforms for
            rough terrain, and \href{https://rtc.ru/solution/agro-robot/}{educational platforms}
        \end{itemize}

        \subsection*{Engineer \hfill {\color{gray}Sep 2016 – Jun 2018}}
        \href{https://en.itmo.ru/}{ITMO University}
        \begin{itemize}
            \item Took part in the development team of a mobile robotic
            platform designed for remote inspection of industrial premises.
            Engaged in the development of a controller for BLDC motors.
            The task included obtaining data from encoders, and PID speed control based on them
        \end{itemize}
    \end{changemargin}

    \section*{Education}    
    \begin{minipage}[t]{0.5\linewidth}
        \subsection*{Master's Degree \hfill {\color{gray}2016 – 2018}}
        \href{https://en.itmo.ru/}{ITMO University}
        \begin{itemize}
            \item Degree program of Digital control in modern technics
            \item Diploma with Honors
            \item GPA 4.8 of 5
        \end{itemize}
    \end{minipage}
    \hfill%
    \begin{minipage}[t]{0.45\linewidth}
        \subsection*{Bachelor's Degree \hfill {\color{gray}2012 – 2016}}
        \href{https://en.itmo.ru/}{ITMO University}
        \begin{itemize}
            \item Degree program of Control in technical systems
            \item GPA 4.76 
        \end{itemize}
    \end{minipage}
\end{document}
